UGAN: Underwater Image Restoration using Generative Adversarial Networks

### 2017-09-12 files/paper/paper.tex
update

\section{Introduction}
TODO - talk about having to go back to the same location if you want to get good/bad pairs of the "same" image.
Vision is a commonly used sensor in autonomous underwater robots due to its non-intrusive, passive, and energy
effecient nature. The monitoring of coral reefs \cite{shkurti2012multi}, deep ocean exploration
\cite{whitcomb2000advances}, and mapping of the seabed are all tasks suitable for autonomous robots because they
provide safety by taking the risk instead of a human. Despite the advantages vision provides, many underwater
environments can be quite noisy due to light refraction and particles present in the water. Because red wavelengths are
quickly absorbed by water, images tend to have a green or blue hue to them. As you go deeper, this worsens as more
and more red wavelengths are being absorbed. This extremely non-linear distortion has many factors such as the amount
of light present (overcast vs sunny or depth), particles in the water, time of day, and the camera being used. This may
cause difficulty in tasks such as segmentation, tracking, or classification due to their indirect or direct use of
color.

@@

   \includegraphics[width=0.8in]{n01496331_175_B} &
   \includegraphics[width=0.8in]{n01664065_4022_B} &
   \includegraphics[width=0.8in]{n01917289_889_B} &
   \includegraphics[width=0.8in]{n01914609_116_B} \\
   \includegraphics[width=0.8in]{n01496331_175_A} &
   \includegraphics[width=0.8in]{n01664065_4022_A} &
   \includegraphics[width=0.8in]{n01917289_889_A} &
   \includegraphics[width=0.8in]{n01914609_116_A} \\

@@

\begin{equation}
\begin{aligned}
   \mathcal{L}_{WGAN}(G,D) = \mathbb{E} [D(I^C)] - \mathbb{E} & [D(G(I^D))] + \\
   \lambda \mathbb{E} & _{\hat{x} \sim \mathbb{P}_{\hat{x}}} [(|| \nabla_{\hat{x}} D(\hat{x})||_2 -1)^2 ],
\end{aligned}
\end{equation}

@@

\noindent where $\mathbb{P}_{\hat{x}}$ is defined as samples along straight lines between pairs of points coming from
the true data distribution and the generator distribution, and $\lambda$ is a weighing factor. In order to give $G$
some sense of ground truth, as well as capture low level frequencies in the image, we also consider the $L1$ loss

@@

\begin{equation}
   \begin{aligned}
      \mathcal{L}_{UGAN}^* = \min\limits_{G}\max\limits_{D} \mathcal{L}_{WGAN}(G,D) + \mathcal{L}_{L1}(G).
   \end{aligned}
\end{equation}

@@

\begin{equation}
   \begin{aligned}
      \mathcal{L}_{UGAN}^* = \min\limits_{G}\max\limits_{D} \mathcal{L}_{WGAN}(G,D) + \mathcal{L}_{L1}(G) + \mathcal{L}_{GDL}
   \end{aligned}
\end{equation}

@@

Our discriminator is modeled after that of \cite{radford2015unsupervised}, except no batch normalization is used. This
is due to the fact that we penalize the norm of the discriminator's gradient with respect to each input individually,
which batch normalization would invalidate. The authors of \cite{gulrajani2017improved} recommend layer normalization
\cite{ba2016layer}, but we found no significant improvements. In all of our experiments, we use $\lambda_{L1} = 100$,
$\lambda_{GP} = 10$, batch size of 32, Adam Optimizer \cite{kingma2014adam} with learning rate $1e-4$, and train for 100 epochs.
Following WGAN-GP, the discriminator is updated $n$ times for every update of the generator, where $n = 5$.
For UGAN-P, we set $\lambda_{IG} = 1.0$.
Our implementation was done using the Tensorflow library \cite{abadi2016tensorflow}.
\footnote{Code is available at https://github.com/cameronfabbri/Underwater-Color-Correction}

@@

%\footnote{Code for inception score can be found at https://github.com/openai/improved-gan}
%\begin{center}
%\begin{tabular}{c c c c c c}
%Samples & real & ugan & ugan-p & cyclegan \\ \hline
%Model & True Images & UGAN & UGAN-P & CycleGAN \\ \hline
%Score $\pm$ std. & $5.69 \pm 0.23$ & $6.18 \pm 0.35$ & $6.30 \pm 0.32$ & $6.37 \pm 0.43$ \\ \hline
%\end{tabular}
%\end{center}

\subsection{Comparison to CycleGAN}

It is important to note that during the process of learning a mapping $F: X \rightarrow Y$, CycleGAN also learns a
mapping $G: Y \rightarrow X$. Here we show that UGAN and UGAN-P provide superior performance.
Here I want to show a number of things. First talk about the datasets used, Imagenet and the diving videos.
Second, show some general results. Explain how our network is able to do three very important things: 1) Restore an
image to its natural colors with varying amounts of distortion, i.e. blue hue, green hue, aka not just one type of
color distortion. 2) The network does not just subtract a certain hue from the entire image. Show how in the clownfish
image, part of the image has good colors, while part of it doesn't. Our network is able to leave correct colors. Third,
show that even images taken towards the water's surface, either above or below, are able to be restored correctly.

@@

   \includegraphics[width=0.8in]{n01496331_15872_original} &
   \includegraphics[width=0.8in]{n01496331_15872_cimg}     &
   \includegraphics[width=0.8in]{n01496331_15872_u0img}    &
   \includegraphics[width=0.8in]{n01496331_15872_u1img}    \\ [-1ex]
   \includegraphics[width=0.8in]{n01496331_15872_oedges}   &
   \includegraphics[width=0.8in]{n01496331_15872_cedges}   &
   \includegraphics[width=0.8in]{n01496331_15872_u0edges}  &
   \includegraphics[width=0.8in]{n01496331_15872_u1edges}  \\
   0 & \small{125.78} & \small{80.68} & \small{78.49} \\

   \includegraphics[width=0.8in]{n01496331_22079_original} &
   \includegraphics[width=0.8in]{n01496331_22079_cimg}     & 
   \includegraphics[width=0.8in]{n01496331_22079_u0img}    &
   \includegraphics[width=0.8in]{n01496331_22079_u1img}    \\ [-1ex]
   \includegraphics[width=0.8in]{n01496331_22079_oedges}   &
   \includegraphics[width=0.8in]{n01496331_22079_cedges}   &
   \includegraphics[width=0.8in]{n01496331_22079_u0edges}  &
   \includegraphics[width=0.8in]{n01496331_22079_u1edges}  \\
   0 & \small{94.57} & \small{38.22} & \small{37.29} \\

   \includegraphics[width=0.8in]{n02607072_4739_original} &
   \includegraphics[width=0.8in]{n02607072_4739_cimg} &
   \includegraphics[width=0.8in]{n02607072_4739_u0img} &
   \includegraphics[width=0.8in]{n02607072_4739_u1img} \\ [-1ex]
   \includegraphics[width=0.8in]{n02607072_4739_oedges} &
   \includegraphics[width=0.8in]{n02607072_4739_cedges} &
   \includegraphics[width=0.8in]{n02607072_4739_u0edges} &
   \includegraphics[width=0.8in]{n02607072_4739_u1edges} \\
   0 & \small{100.69} & \small{87.81} & \small{87.95} \\

@@

%
%\begin{thebibliography}{1}
%\bibitem{hires}{Johnson‐Roberson, Matthew, et al. "High‐Resolution Underwater Robotic Vision‐Based Mapping and Three‐Dimensional Reconstruction for Archaeology." Journal of Field Robotics 34.4 (2017): 625-643.}
%
%\bibitem{col1}{Zhang, Richard, Phillip Isola, and Alexei A. Efros. "Colorful image colorization." European Conference on Computer Vision. Springer International Publishing, 2016.}

%\bibitem{col2}{Cheng, Zezhou, Qingxiong Yang, and Bin Sheng. "Deep colorization." Proceedings of the IEEE International Conference on Computer Vision. 2015.}

%\bibitem{col3}{Iizuka, Satoshi, Edgar Simo-Serra, and Hiroshi Ishikawa. "Let there be color!: joint end-to-end learning of global and local image priors for automatic image colorization with simultaneous classification." ACM Transactions on Graphics (TOG) 35.4 (2016): 110.}

%\bibitem{pix2pix}{Isola, Phillip, et al. "Image-to-image translation with conditional adversarial networks." arXiv preprint arXiv:1611.07004 (2016).}

%\bibitem{watergan}{Li, Jie, et al. "WaterGAN: Unsupervised Generative Network to Enable Real-time Color Correction of Monocular Underwater Images." arXiv preprint arXiv:1702.07392 (2017).}

%\end{thebibliography}

%\bibliography{/home/fabbric/Research/colorCorrection/files/paper/cambibs}
\bibliography{cambibs}
\bibliographystyle{ieeetr}

% that's all folks
\end{document}

>>>>

\section{Introduction}
TODO - talk about having to go back to the same location if you want to get good/bad pairs of the ``same'' image.
Vision is a commonly used sensor in autonomous underwater robots due to its non-intrusive, passive, and energy
effecient nature. The monitoring of coral reefs \cite{shkurti2012multi}, deep ocean exploration
\cite{whitcomb2000advances}, and mapping of the seabed are all tasks suitable for autonomous robots because they
provide safety by taking the risk instead of a human. Despite the advantages vision provides, many underwater
environments can be quite noisy due to light refraction and particles present in the water. Because red wavelengths are
quickly absorbed by water, images tend to have a green or blue hue to them. As you go deeper, this worsens as more
and more red wavelengths are being absorbed. This extremely non-linear distortion has many factors such as the amount
of light present (overcast vs sunny or depth), particles in the water, time of day, and the camera being used. This may
cause difficulty in tasks such as segmentation, tracking, or classification due to their indirect or direct use of
color.

@@

   \includegraphics[width=0.8in]{n01496331_873_X} &
   \includegraphics[width=0.8in]{n01664065_4022_X} &
   \includegraphics[width=0.8in]{n01917289_889_X} &
   \includegraphics[width=0.8in]{n01914609_116_X} \\
   \includegraphics[width=0.8in]{n01496331_873_Y} &
   \includegraphics[width=0.8in]{n01664065_4022_Y} &
   \includegraphics[width=0.8in]{n01917289_889_Y} &
   \includegraphics[width=0.8in]{n01914609_116_Y} \\

@@

\begin{equation}
\begin{aligned}
   \mathcal{L}_{WGAN}(G,D) = \mathbb{E} [D(I^C)] - \mathbb{E} & [D(G(I^D))] + \\
   \lambda_{GP} \mathbb{E} & _{\hat{x} \sim \mathbb{P}_{\hat{x}}} [(|| \nabla_{\hat{x}} D(\hat{x})||_2 -1)^2 ],
\end{aligned}
\end{equation}

@@

\noindent where $\mathbb{P}_{\hat{x}}$ is defined as samples along straight lines between pairs of points coming from
the true data distribution and the generator distribution, and $\lambda_{GP}$ is a weighing factor. In order to give $G$
some sense of ground truth, as well as capture low level frequencies in the image, we also consider the $L1$ loss

@@

\begin{equation}
   \begin{aligned}
      \mathcal{L}_{UGAN}^* = \min\limits_{G}\max\limits_{D} \mathcal{L}_{WGAN}(G,D) + \lambda_{1} \mathcal{L}_{L1}(G).
   \end{aligned}
\end{equation}

@@

\begin{equation}
   \begin{aligned}
      \mathcal{L}_{UGAN}^* = \min\limits_{G}\max\limits_{D} \mathcal{L}_{WGAN}(G,D) + \lambda_{1} \mathcal{L}_{L1}(G) +  \lambda_{2} \mathcal{L}_{GDL}
   \end{aligned}
\end{equation}

@@

Our discriminator is modeled after that of \cite{radford2015unsupervised}, except no batch normalization is used. This
is due to the fact that we penalize the norm of the discriminator's gradient with respect to each input individually,
which batch normalization would invalidate. The authors of \cite{gulrajani2017improved} recommend layer normalization
\cite{ba2016layer}, but we found no significant improvements. In all of our experiments, we use $\lambda_{1} = 100$,
$\lambda_{GP} = 10$, batch size of 32, Adam Optimizer \cite{kingma2014adam} with learning rate $1e-4$, and train for 100 epochs.
Following WGAN-GP, the discriminator is updated $n$ times for every update of the generator, where $n = 5$.
For UGAN-P, we set $\lambda_{2} = 1.0$.
Our implementation was done using the Tensorflow library \cite{abadi2016tensorflow}.
\footnote{Code is available at https://github.com/cameronfabbri/Underwater-Color-Correction}

@@

While many of the distorted images in the test set contain a blue or green hue, that is not always the case. In certain
environments, it is possible that objects close to the camera are undistorted with correct colors, while the background
of the image contains distortion. In these cases, we would like the network to only correct parts of the image that
appear distorted. Figure X shows a sample of such an image, which implies it does not simply subtract a variable
amount of green or blue from the entire image.

% Directly from the first paper on the inception score: We find that it’s important to evaluate the metric on a large
% enough number of samples (i.e. 50k) as part of this metric measures diversity.
% % Therefore we should not include it I think
% \footnote{Code for inception score can be found at https://github.com/openai/improved-gan}
%\begin{center}
%\begin{tabular}{c c c c c c}
%Samples & real & ugan & ugan-p & cyclegan \\ \hline
%Model & True Images & UGAN & UGAN-P & CycleGAN \\ \hline
%Score $\pm$ std. & $5.69 \pm 0.23$ & $6.18 \pm 0.35$ & $6.30 \pm 0.32$ & $6.37 \pm 0.43$ \\ \hline
%\end{tabular}
%\end{center}

\subsection{Comparison to CycleGAN}
\textbf{note also this is on cyclegan's training set - retraining now with a test set in mind....should be quick.}
It is important to note that during the process of learning a mapping $F: X \rightarrow Y$, CycleGAN also learns a
mapping $G: Y \rightarrow X$. Here we show that UGAN and UGAN-P provide superior performance.
Second, show some general results. Explain how our network is able to do three very important things: 1) Restore an
image to its natural colors with varying amounts of distortion, i.e. blue hue, green hue, aka not just one type of
color distortion. 2) The network does not just subtract a certain hue from the entire image. Show how in the clownfish
image, part of the image has good colors, while part of it doesn't. Our network is able to leave correct colors. Third,
show that even images taken towards the water's surface, either above or below, are able to be restored correctly.

@@

%   \includegraphics[width=0.8in]{n01496331_15872_original} &
%   \includegraphics[width=0.8in]{n01496331_15872_cimg}     &
%   \includegraphics[width=0.8in]{n01496331_15872_u0img}    &
%   \includegraphics[width=0.8in]{n01496331_15872_u1img}    \\ [-1ex]
%   \includegraphics[width=0.8in]{n01496331_15872_oedges}   &
%   \includegraphics[width=0.8in]{n01496331_15872_cedges}   &
%   \includegraphics[width=0.8in]{n01496331_15872_u0edges}  &
%   \includegraphics[width=0.8in]{n01496331_15872_u1edges}  \\
   0 & \small{125.78} & \small{80.68} & \small{78.49} \\

%   \includegraphics[width=0.8in]{n01496331_22079_original} &
%   \includegraphics[width=0.8in]{n01496331_22079_cimg}     & 
%   \includegraphics[width=0.8in]{n01496331_22079_u0img}    &
%   \includegraphics[width=0.8in]{n01496331_22079_u1img}    \\ [-1ex]
%   \includegraphics[width=0.8in]{n01496331_22079_oedges}   &
%   \includegraphics[width=0.8in]{n01496331_22079_cedges}   &
%   \includegraphics[width=0.8in]{n01496331_22079_u0edges}  &
%   \includegraphics[width=0.8in]{n01496331_22079_u1edges}  \\
   0 & \small{94.57} & \small{38.22} & \small{37.29} \\

%   \includegraphics[width=0.8in]{n02607072_4739_original} &
%   \includegraphics[width=0.8in]{n02607072_4739_cimg} &
%   \includegraphics[width=0.8in]{n02607072_4739_u0img} &
%   \includegraphics[width=0.8in]{n02607072_4739_u1img} \\ [-1ex]
%   \includegraphics[width=0.8in]{n02607072_4739_oedges} &
%   \includegraphics[width=0.8in]{n02607072_4739_cedges} &
%   \includegraphics[width=0.8in]{n02607072_4739_u0edges} &
%   \includegraphics[width=0.8in]{n02607072_4739_u1edges} \\
   0 & \small{100.69} & \small{87.81} & \small{87.95} \\

@@

\bibliography{cambibs}
\bibliographystyle{ieeetr}

\end{document}
